---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(dplyr)
library(tidyverse)
```


```{r}
AuxinMip <-read.csv(file = "/media/cunzac/bioinformatica/mbarrios/proyectos/katia/tarea1/Hormone_nets/AuxinMip.tsv", sep = "\t", header=F)

BrassinoMip <-read.csv(file = "/media/cunzac/bioinformatica/mbarrios/proyectos/katia/tarea1/Hormone_nets/BrassinoMip.tsv", sep = "\t", header=F)

MYCMip <-read.csv(file = "/media/cunzac/bioinformatica/mbarrios/proyectos/katia/tarea1/Hormone_nets/MYC2_net.tsv", sep = "\t", header=F)



AuxinMip
BrassinoMip
MYCMip
```


Obtener reguladores y regulones unicos

cut -f1 Hormone_nets/AuxinMip.tsv | sort | uniq > Hormone_nets/col1-AuxinMip.tsv
cut -f3 Hormone_nets/AuxinMip.tsv | sort | uniq > Hormone_nets/col3-AuxinMip.tsv
cut -f1 Hormone_nets/BrassinoMip.tsv | sort | uniq > Hormone_nets/col1-BrassinoMip.tsv
cut -f3 Hormone_nets/BrassinoMip.tsv | sort | uniq > Hormone_nets/col3-BrassinoMip.tsv
cut -f1 Hormone_nets/MYC2_net.tsv | sort | uniq > Hormone_nets/col1-MYC2_net.tsv
cut -f3 Hormone_nets/MYC2_net.tsv | sort | uniq > Hormone_nets/col3-MYC2_net.tsv

```{r}
AuxinMipV1 <-AuxinMip %>% 
  select(V1) %>%
  arrange() %>%
  unique

AuxinMipV3 <-AuxinMip %>% 
  select(V3) %>%
  arrange() %>%
  unique

BrassinoMipV1 <-BrassinoMip %>% 
  select(V1) %>%
  arrange() %>%
  unique

BrassinoMipV3 <-BrassinoMip %>% 
  select(V3) %>%
  arrange() %>%
  unique

MYCMipV1 <-MYCMip %>% 
  select(V1) %>%
  arrange() %>%
  unique

MYCMipV3 <-MYCMip %>% 
  select(V3) %>%
  arrange() %>%
  unique
```


```{r}

```












```{r}
aux_tomato_sano_regulador<-read.csv("../tarea3/Auxin_regulatoryNetwork_healthy.tsv", header=F, sep='\t')
aux_tomato_sano_regulador

families <- read.csv("../tarea3/Sly_TF_list.txt", header=TRUE, sep='\t') %>%
  select(-1) %>% 
  mutate(across(everything(), ~ str_replace(., "\\.\\d+$", "")))
families



dict_fam<-setNames(families$Family,families$Gene_ID)
str(dict_fam)

dict_fam

aux_tomato_sano_regulador_fam<-aux_tomato_sano_regulador%>%
  mutate(FT = recode(V1, !!!dict_fam, .default = "none")) %>%
  rename(regulador = V1,
         estado_1 = V2,
         regulon = V3,
         estado_2 = V4
         )
aux_tomato_sano_regulador_fam


write.table(aux_tomato_sano_regulador_fam, "../tarea3/Auxin_regulatoryNetwork_healthy_fam.tsv", 
            sep = "\t", row.names = FALSE, col.names=TRUE, quote = FALSE)

```
